Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-02 paper/paper.Rmd
Make bayes factor plot

d <- left_join(project_plan, project_data_summary)
```

@@

```{r}
BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
```
@etz2016

>>>>

d <- left_join(project_plan, project_data_summary, by = c("project_key"))
```

@@

```{r}
getBF <- function(t_stat, t_df) {
  return(log10(ttest.tstat(t = t_stat, n1 = t_df, rscale = 1, simple = T)))
};

tstatDF <- d %>%
  filter(original_t_stat != "NA") %>%
  select(project_key, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
  rowwise() %>%
  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
  rowwise() %>%
  mutate(repBF = getBF(rep_t_stat, rep_t_df))

ggplot(tstatDF, aes(x = origBF, y = repBF, size = rep_t_df/original_t_df)) +
  geom_point()+
  theme_bw()+
  xlim(-2, 30) +
  ylim(-2, 30) +
  geom_hline(aes(yintercept = 10), linetype = 2)+
  geom_hline(aes(yintercept = 3), linetype = 2)+
  geom_hline(aes(yintercept = 1/3), linetype = 2)+
  geom_hline(aes(yintercept = 1/10), linetype = 2)+
  geom_vline(aes(xintercept = 10), linetype = 2)+
  geom_vline(aes(xintercept = 3), linetype = 2)+
  geom_vline(aes(xintercept = 1/3), linetype = 2)+
  geom_vline(aes(xintercept = 1/10), linetype = 2)

  # scale_x_log10(limits = c(-50, 100)) +
  # scale_y_log10(limits = c(-50, 10))

```
@etz2016
